---
output: html_document
editor_options: 
  chunk_output_type: console
---
Lesson 7
========================================================
# Installing packages
```{r Installing packages}
setwd("C:/Users/maru/Documents/dsNanodegree/machine-learning-master/projects/finding_donors/dataAnalysisR/")
pf <- read.delim('pseudo_facebook.tsv')
#install.packages('ggplot2')
#install.packages('dplyr')
library(ggplot2)
suppressMessages(library(dplyr))
```
### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes:

***

### Third Qualitative Variable
Notes:

```{r Third Qualitative Variable}
pf.fc_by_age_gender <- pf %>%
  filter(!is.na(gender)) %>%
  group_by(age, gender) %>%
  summarise(mean_friend_count = mean(friend_count),
            median_friend_count = median(friend_count),
            n = n()) %>%
  ungroup() %>%
  arrange(age)

head(pf.fc_by_age_gender)
```

***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}
ggplot(aes(x=age, y=median_friend_count), data=pf.fc_by_age_gender) +
  geom_line(aes(color=gender))
```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***

### Reshaping Data
Notes:

```{r}
#install.packages('reshape2')
#library(reshape2)

pf.fc_by_age_gender.wide <- dcast(pf.fc_by_age_gender, age ~ gender, value.var = 'median_friend_count')

head(pf.fc_by_age_gender.wide)
```


***

### Ratio Plot
Notes:

```{r Ratio Plot}
ggplot(aes(x=age, y=female/male),
       data=pf.fc_by_age_gender.wide) +
  geom_line() +
  geom_hline(yintercept = 1, alpha = 0.3, linetype = 2)
```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}
pf$year_joined <- floor(2014 - pf$tenure/365)
```

***

### Cut a Variable
Notes:

```{r Cut a Variable}
pf$year_joined.bucket <- cut(pf$year_joined, breaks=c(2004, 2009, 2011, 2012, 2014))
```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}
ggplot(aes(x=age, y=friend_count), 
       data = subset(pf, !is.na(year_joined.bucket))) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary', fun.y = median)
```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}
ggplot(aes(x=age, y=friend_count), 
       data = subset(pf, !is.na(year_joined.bucket))) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary', fun.y = median) +
  geom_line(stat = 'summary', fun.y = mean, linetype = 2)

```

***

### Friending Rate
Notes:

```{r Friending Rate}
with(subset(pf, tenure >= 1), summary(friend_count / tenure))
```

***

### Friendships Initiated
Notes:

What is the median friend rate?
0.2205
What is the maximum friend rate?
417
```{r Friendships Initiated}
ggplot(aes(x=tenure, y=friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket))
```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}
ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_smooth(aes(color = year_joined.bucket))

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}
yo <- read.csv('yogurt.csv')
str(yo)

# Change the id from an int to a factor
yo$id <- factor(yo$id)
str(yo)

#ggplot(aes(x=price), data = yo) +
  geom_histogram(binwidth = 5)

hist(yo$price)
```

***

### Number of Purchases
Notes:

```{r Number of Purchases}
#summary(yo)
#length(unique(yo$price))
#table(yo$price)

yo <- transform(yo, all.purchases = strawberry + blueberry + pina.colada + plain + mixed.berry)

summary(yo$all.purchase)

yo$all.purchases <- yo$strawberry + yo$blueberry + yo$pina.colada + yo$plain + yo$mixed.berry

```

***

### Prices over Time
Notes:

```{r Prices over Time}
ggplot(aes(x = time, y = price), data = yo) +
  geom_point()
```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}
set.seed(0)
sample.ids <- sample(levels(yo$id),16)

ggplot(aes(x = time, y = price),
data = subset(yo, id %in% sample.ids))+
facet_wrap(~ id)+
geom_line()+
geom_point(aes(size = all.purchase,), pch = 1)
```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:

***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

