---
output: html_document
editor_options: 
  chunk_output_type: console
---
Lesson 5
========================================================

setwd("C:/Users/maru/Documents/dsNanodegree/machine-learning-master/projects/finding_donors/dataAnalysisR/")
pf <- read.csv('pseudo_facebook.tsv', sep='\t')
install.packages('ggplot2')
library(ggplot2)

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}

```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}

```

***

### Overplotting
Notes:

```{r Overplotting}

```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}

```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}

```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}

```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
install.packages('dplyr')
library(dplyr)

pf.fc_by_age <- pf %>%
  group_by(age) %>%
  summarize(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age) 
head(pf.fc_by_age, 20)
```

Create your plot!

```{r Conditional Means Plot}
library(ggplot2)
ggplot(data = pf.fc_by_age, aes(y=friend_count_mean, x = age)) + geom_line()
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(aes(x=age, y=friend_count), data=pf) +
  xlim(13,70) + ylim(0, 1000) +
  geom_point(alpha = 0.05, position = position_jitter(h=0), color='orange') +
  coord_trans(y='sqrt') +
  geom_line(stat='summary', fun.y=mean) +
  geom_line(stat='summary', fun.y=quantile, fun.args=list(probs=0.1), linetype=2, color='blue') +
  geom_line(stat='summary', fun.y=quantile, fun.args=list(probs=0.5), color='blue') +
  geom_line(stat='summary', fun.y=quantile, fun.args=list(probs=0.9), linetype=2, color='blue')  


```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
cor.test(pf$age, pf$friend_count)
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets, message=FALSE, warning=FALSE, paged.print=FALSE}
with(subset(pf, age<=70)                 , cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:
```{r Correlation on Subsets, message=FALSE, warning=FALSE, paged.print=FALSE}
with(subset(pf, age<=70)                 , cor.test(age, friend_count, method='spearman'))
```

***

## Create Scatterplots
Notes:

```{r}
ggplot(aes(x=www_likes_received, y=likes_received), data=pf) + geom_point()
```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
ggplot(aes(x=www_likes_received, y=likes_received), data=pf) + geom_point() +
  xlim(0, quantile(pf$www_likes_received, 0.95)) +
  ylim(0, quantile(pf$likes_received, 0.95)) +
  geom_smooth(method = 'lm', color = 'red')
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}
with(pf, cor.test(www_likes_received, likes_received))
```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

```{r load data base mitchel}
data(Mitchell)
```

Create your plot!

```{r Temp vs Month}
ggplot(data=Mitchell, aes(x=Month, y=Temp)) +
  geom_point()
```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}
with(Mitchell, cor.test(Month, Temp))
```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}
ggplot(data=Mitchell, aes(x=Month, y=Temp)) +
  geom_point() +
  scale_x_discrete(breaks=seq(0, 203, 12))
```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:
```{r A New Perspective}
ggplot(data=Mitchell, aes(x=(Month%%12), y=Temp)) +
  geom_point()
```
***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
pf$age_with_months <- pf$age + (1 - pf$dob_month / 12 )
```

***

### Age with Months Means

```{r Age with Months Means}
pf.fc_by_age_months <- pf %>%
  group_by(age_with_months) %>%
  summarize(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age_with_months)

head(pf.fc_by_age_months)
```

### Age with Months Means Alternate Solution

```{r Age with Months Means}
age_with_months_groups <- group_by(pf, age_with_months)

pf.fc_by_age_months2 <- summarize( age_with_months_groups, friend_count_mean = mean(friend_count), friend_count_median = median(friend_count), n = n())

pf.fc_by_age_months2 <- arrange(pf.fc_by_age_months2, age_with_months)

head(pf.fc_by_age_months2)

```

Programming Assignment
```{r Programming Assignment}


```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

